Outline paper - Multiple imputation for statistical disclosure control: Creating synthetic datasets with *mice*

### 2021-01-11 mice_synthesizing/paper.Rmd
Add van buuren fcs reference.

The `mice` package has been developed for multiple imputation of missing data. In this context, the aim is to replace missing values due to nonresponse by plausible values from the posterior predictive distribution of the variable containing the missings. Doing so, `mice` makes use of fully conditional specification (FCS) [**ref to Stef's paper in 2006**], which breaks down the multivariate distribution of the data $\textbf{Y} = (\textbf{Y}_{obs}, \textbf{Y}_{mis})$ into $j = 1, 2, \dots, k$ univariate conditional densities, with $k$ the number of variables in the data. Using FCS, for every variable containing missing values a model is constructed, to impute the missing values $Y_{j, mis}$ with draws from the posterior predictive distribution of $P(Y_{j, mis} | \textbf{Y}_{obs}, \theta)$ on a variable by variable basis. Note that the predictor matrix $Y_{-j}$ may contain yet imputed values from an earlier imputation step, and thus will be updated after every iteration. This procedure is applied $m$ times, resulting in $m$ completed datasets $\textbf{D} = (\textbf{D}^{(1)}, \textbf{D}^{(2)}, \dots, \textbf{D}^{(m)})$, with $\textbf{D}^{(l)} = (\textbf{Y}_{obs}, Y^{(l)}_{mis})$. __MAYBE ADD AN EXAMPLE OF HOW TO DO IT IN `mice`__

__DISCUSS ESTIMATORS FOR MISSING AT A LATER POINT__

>>>>

The `mice` package has been developed for multiple imputation of missing data. In this context, the aim is to replace missing values due to nonresponse by plausible values from the posterior predictive distribution of the variable containing the missings. Doing so, `mice` makes use of fully conditional specification [FCS; @vanbuuren_fully_2006], which breaks down the multivariate distribution of the data $\textbf{Y} = (\textbf{Y}_{obs}, \textbf{Y}_{mis})$ into $j = 1, 2, \dots, k$ univariate conditional densities, with $k$ the number of variables in the data. Using FCS, for every variable containing missing values a model is constructed, to impute the missing values $Y_{j, mis}$ with draws from the posterior predictive distribution of $P(Y_{j, mis} | \textbf{Y}_{obs}, \theta)$ on a variable by variable basis. Note that the predictor matrix $Y_{-j}$ may contain yet imputed values from an earlier imputation step, and thus will be updated after every iteration. This procedure is applied $m$ times, resulting in $m$ completed datasets $\textbf{D} = (\textbf{D}^{(1)}, \textbf{D}^{(2)}, \dots, \textbf{D}^{(m)})$, with $\textbf{D}^{(l)} = (\textbf{Y}_{obs}, Y^{(l)}_{mis})$. __MAYBE ADD AN EXAMPLE OF HOW TO DO IT IN `mice`__
